Alleviating the Topology Mismatch Problem in Distributed Overlay Networks

### 2015-05-11 intro.tex
2015.04.24 (Vassilis) Added one paper from 2014. Refreshed some of the references (i.e., total skype users and p2p traffic future projection). Updated a conference paper to a more recent journal paper. Fine-tuned the typesetting, especially for tabular data.

The peer-to-peer paradigm gave impetus to two ``killer'' applications:
file-sharing and Internet telephony.
The {\sl Napster} file-sharing system was widely acknowledged as the 
``fastest growing Internet application ever'' in $2001$ when it topped
$26$ million users sharing over $80$ million songs.
Other file-sharing applications followed suit, 
including {\sl Gnutella} and {\sl Limewire} enjoying $3$ 
million concurrently-connected peers, as well as 
{\sl BitTorrent} connecting over $150$ million monthly users by January $2012$~\cite{bittorrentusers}.
\p\ telephony saw explosive growth with the advent of {\sl Skype}.
Since its introduction in $2003$,
{\sl Skype} has become extremely popular with more than $650$ million users 
in $2011$~\cite{skypetotalusers} while on January $21$st, $2013$,
the astonishing figure of $50$ million concurrently-online users
was reported~\cite{skypesymusers}.
%%
Apart from the above, a startling number of diverse and successful
applications have been built based on \p\ architectures. Some of them include:
distributed search engines~\cite{yaci}, 
distributed data-storage systems~\cite{kbc_oceanstore_2000,bdet_fsdfs_2000,dkkms_cfs_2001,dr_pastutility_2001,abc_farsite_2002,mmfc_ivy_2002,arla,agebh_dks_2003},
Web caches, archives and publishing systems~\cite{ird_squirrel_2002,bags_youserv_2002,wrc_publius_2000,wm_tangler_2001},
messaging and dissemination applications~\cite{threedegrees,icpp08-pd}, 
event-notification infrastructures~\cite{rkcd_scribe_2001,cdkr_scribe_2002,agebh_dks_2003}, 
naming services~\cite{cmm_chorddns_2002}, 
censor-resistant stores~\cite{cswh_freenet_2001} and
lately, even cloud-based platforms~\cite{mgpj_cloudsnap_2011}.

@@

The single key issue that determines the efficiency of an overlay network,
is how well the overlay maps to the underlying network topology on which it
``rests''. 
Consider two nodes\footnote{In \p\ networks,
the participating nodes are typically user-PCs operating at the edge of the
Internet.} that are connected with each other via a path of overlay links.
If the application running on the nodes, generates heavy traffic along
the overlay path, it would be beneficial to
construct the overlay topology in a way that the number of 
underlying IP links between these two nodes is minimized.
Should the overlay network be constructed so that
it does not match the underlying topology well, 
the inherent \emph{topology mismatch} gives two
significant problems. First, the performance of the application per se, can be
adversely affected since traffic must flow over a larger,
redundant, number of physical hops resulting in poor user experience 
entailing noticeable latencies or jittering. 
%%
Second, other applications running
on the underlying network infrastructure are also adversely affected.
Studies have shown that highly popular \p\ applications contribute 
the largest portion of the overall 
Internet traffic~\cite{seroiu_analysiscds_2002,sen_analyzep2ptraffic_2004,krp_ispfear_2005}, with some reporting that more than $60$\% of this traffic 
to be \p-related~\cite{cachelogic,ipoque2007,ipoque2009};
it was also projected that this traffic would reach
$8\;$\emph{Petabytes}-per-month by the end of $2012$~\cite{multinteligence}. 
Evidently, this constitutes a major burden for 
Internet Service Providers (ISPs) who must route 
all of this traffic to destinations at the edge of the Internet. 
If the \p\ overlay topology is poorly designed, 
the demand on the Internet's backbone infrastructure may 
substantially increase as traffic might have to flow
``back and forth'' several times between two neighboring ISPs
while trying to travel from the source to its destination node
in the overlay.
Hence, it is critical that \p\ networks be laid out 
in ways that their topology matches, as closely as possible, the 
underlying IP topology.

>>>>

The peer-to-peer paradigm gave impetus to two ``killer'' applications:
file-sharing and Internet telephony.
The {\sl Napster} file-sharing system was widely acknowledged as the 
``fastest growing Internet application ever'' in $2001$ when it topped
$26$ million users sharing over $80$ million songs.
Other file-sharing applications followed suit, 
including {\sl Gnutella} and {\sl Limewire} enjoying $3$ 
million concurrently-connected peers, as well as 
{\sl BitTorrent} connecting over $150$ million monthly users by January $2012$~\cite{bittorrentusers}.
\p\ telephony saw explosive growth with the advent of {\sl Skype}.
Since its introduction in $2003$,
{\sl Skype} has become extremely popular with more than $650$ million users 
in $2011$~\cite{skypetotalusers}, an astonishing $50$+ million concurrently-online
users~\cite{skypesymusers} and slowly but steadily replacing traditional
carrier traffic for services like telephony services, which was recently estimated to
have reached 214 billion minutes for year 2013~\cite{skypetraffic}.

%%
Apart from the above, a startling number of diverse and successful
applications have been built based on \p\ architectures. Some of them include:
distributed search engines~\cite{yaci}, 
distributed data-storage systems~\cite{kbc_oceanstore_2000,bdet_fsdfs_2000,dkkms_cfs_2001,dr_pastutility_2001,abc_farsite_2002,mmfc_ivy_2002,arla,agebh_dks_2003},
Web caches, archives and publishing systems~\cite{ird_squirrel_2002,bags_youserv_2002,wrc_publius_2000,wm_tangler_2001},
messaging and dissemination applications~\cite{threedegrees,icpp08-pd}, 
event-notification infrastructures~\cite{rkcd_scribe_2001,cdkr_scribe_2002,agebh_dks_2003}, 
naming services~\cite{cmm_chorddns_2002}, 
censor-resistant stores~\cite{cswh_freenet_2001} and
lately, even cloud-based platforms~\cite{mgpj_cloudsnap_2011}.

@@

The single key issue that determines the efficiency of an overlay network,
is how well the overlay maps to the underlying network topology on which it
``rests''. 
Consider two nodes\footnote{In \p\ networks,
the participating nodes are typically user-PCs operating at the edge of the
Internet.} that are connected with each other via a path of overlay links.
If the application running on the nodes, generates heavy traffic along
the overlay path, it would be beneficial to
construct the overlay topology in a way that the number of 
underlying IP links between these two nodes is minimized.
Should the overlay network be constructed so that
it does not match the underlying topology well, 
the inherent \emph{topology mismatch} gives two
significant problems. First, the performance of the application per se, can be
adversely affected since traffic must flow over a larger,
redundant, number of physical hops resulting in poor user experience 
entailing noticeable latencies or jittering. 
%%
Second, other applications running
on the underlying network infrastructure are also adversely affected.
Studies have shown that highly popular \p\ applications contribute 
the largest portion of the overall 
Internet traffic~\cite{seroiu_analysiscds_2002,sen_analyzep2ptraffic_2004,krp_ispfear_2005}, with some reporting that more than $60$\% of this traffic 
to be \p-related~\cite{cachelogic,ipoque2009};
it was also projected that this traffic would reach
$7$~\emph{Exabytes}-per-month by $2018$~\cite{CVNI2014}! 
Evidently, this constitutes a major burden for 
Internet Service Providers (ISPs) who must route 
all of this traffic to destinations at the edge of the Internet. 
If the \p\ overlay topology is poorly designed, 
the demand on the Internet's backbone infrastructure may 
substantially increase as traffic might have to flow
``back and forth'' several times between two neighboring ISPs
while trying to travel from the source to its destination node
in the overlay.
Hence, it is critical that \p\ networks be laid out 
in ways that their topology matches, as closely as possible, the 
underlying IP topology.

### 2015-05-11 mard-survey.tex
2015.04.24 (Vassilis) Added one paper from 2014. Refreshed some of the references (i.e., total skype users and p2p traffic future projection). Updated a conference paper to a more recent journal paper. Fine-tuned the typesetting, especially for tabular data.

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Alleviating the Topology Mismatch Problem in Distributed Overlay Networks}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Vassilis Moustakas,
        H\"useyin Akcan,
        Mema Roussopoulos,
        and~Alex Delis,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{Vassilis Moustakas, Mema Roussopoulos and Alex Delis are with the Department
of Informatics and Telecommunications, National and Kapodistrian University of Athens,
GR15784, Athens, Greece (e-mail: vsmoustakas@gmail.com, mema@di.uoa.gr, ad@di.uoa.gr.}% <-this % stops a space
\thanks{H\"useyin Akcan is with the Department of Software Engineering,
Izmir University of Economics, Izmir, Turkey (email: huseyin.akcan@ieu.edu.tr).}% <-this % stops a space
\thanks{Manuscript received June 30, 2015; revised July 31, 2015.}}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Distributed systems, peer-to-peer architectures, p2p, overlay network,
topology awareness
\end{IEEEkeywords}

>>>>

\usepackage{adjustbox}

@@

\begin{document}

\newcolumntype{R}[2]{%
    >{\adjustbox{angle=#1,lap=\width-(#2)}\bgroup}%
    l%
    <{\egroup}%
}
\newcommand*\rot{\multicolumn{1}{R{45}{1em}}}% no optional argument here, please!

%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Alleviating the Topology Mismatch Problem in Distributed Overlay Networks}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

\author{Vassilis Moustakas,
        H\"useyin Akcan,
        Mema Roussopoulos,
        and~Alex Delis,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{Vassilis Moustakas, Mema Roussopoulos and Alex Delis are with the Department
of Informatics and Telecommunications, National and Kapodistrian University of Athens,
GR15784, Athens, Greece (e-mails: {vsmoustakas,mema,ad}@di.uoa.gr.}% <-this % stops a space
\thanks{H\"useyin Akcan is with the Department of Software Engineering,
Izmir University of Economics, Izmir, Turkey (email: huseyin.akcan@ieu.edu.tr).}% <-this % stops a space
\thanks{Manuscript received June 30, 2015; revised July 31, 2015.}}

@@

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Distributed systems, peer-to-peer, overlay network, topology mismatch,
topology awareness
\end{IEEEkeywords}

### 2015-05-11 structured.tex
2015.04.24 (Vassilis) Added one paper from 2014. Refreshed some of the references (i.e., total skype users and p2p traffic future projection). Updated a conference paper to a more recent journal paper. Fine-tuned the typesetting, especially for tabular data.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Another work that targets mobile networks is \emph{3D Overlay}~\cite{AOS2014}. As the
name suggests, the logical space of the network is a 3-dimensional space and
the (transient) logical IDs (LIDs) are of the form of tuples of $M$-bit identifiers
for each of the $x$, $y$ and $z$ axes. 
When a peer wants to join the network it broadcasts a join request using
expanded ring search. This ensures to locate peers that are physically adjacent
to itself in the physical space. Peers in the network reply to the request
sending their LID together with the list of their neighbours and the
corresponding distances to them. Upon receiving the replies, the joining peer
stores the information to its routing table thus forming an undirected connected
graph of itself and both its $1$- and $2$-hop neighbours. Using hop distance
obtained by the underlying (MANET) routing algorithm, builds a
minimum spanning tree (MST) with itself as the root node and selects as direct
neighbours the peers that are adjacent in the MST. Moreover, removes all the
peers that were selected as directs during routing table construction but now
found to be not adjacent in the MST. This ensures that neighboring peers on the
overlay are also adjacent in the physical layer. Then the joining peer generates
its LID which puts it in the 3 dimentional space. The LID computation is repeated
as part of the update process that is required as a mechanism to maintain
conectivity and adapt to new network states. Similarly to peer LIDs,
keys of the files stored in the network are also generated within afformentioned
3D space. The peer closest to the key of the file is responsible for it. Thus,
for a peer to search for an object, it needs to generate the key for it and then
forward the query. The neighbour to be forwarded the query, is
selected from the routing table so that its LID and the key of the queried
resource, brings closest the query in every part of the tuple.
The interesting proporty of this algorithm is the construction of a multidimentional
space that results in better load balance and finer grained information to ensure
that each hop on the overlay during object location, is also a step closer physically
toward the node that stores it. On the other hand, the use of TTL for its query messages
renders the network not a pure DHT as it looses the ability that traditional
DHTs have for zero false negative queries. Moreover, as the authors also admit, it
does not adapt quickly to network changes and the evaluation was based on the assumption
of low mobility scenarios. For the above reasons, 3DO exhibits the following performance
with respect to the comparison criteria:

\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% 
low &
% 
low &
% 
medium
\end{tabular}
}
\end{center}

### 2015-05-11 unstructured.tex
2015.04.24 (Vassilis) Added one paper from 2014. Refreshed some of the references (i.e., total skype users and p2p traffic future projection). Updated a conference paper to a more recent journal paper. Fine-tuned the typesetting, especially for tabular data.

The \emph{Scalable Bipartite Overlay (SBO)}~\cite{LXN2004,LXN2007} 
reduces the overhead of creating
and maintaining a minimum spanning tree 
by randomly dividing the nodes into
two groups --\emph{red}s and \emph{white}s-- 
and assigning different tasks to the two groups.
When a peer joins the network, it is randomly assigned with an initial
color (red or white).
Then the network bootstrap host node furnishes the joining peer with a list
of active peers along with their color information. 
The joining peer uses this list to 
establish connections to differently colored peers. 
In this regard, all peers form a a bipartite overlay. 
Using the network delay as a metric, white-peers 
peers measure distances from red counterparts
and report the encountered red neighbors.
Having information on all their $2$-hop neighbors 
($N^2$)
red-peers create minimum spanning trees for the neighbors in question and
assign efficient $2$-hop forwarding paths. This process can render a white
peer $E$ non--forwarding neighbor of the red peer $P$. Direct neighbor
replacement is a process conducted by $E$ in order to replace $P$ with a
$P' \in N^2(P)$ as its new neighbor. This adaptation tackles the
topology mismatch problem by reducing message duplication and shorten response
times caused by the problem identified as \emph{Revisit Not known (RN)}. RN is
the situation when a node is visited some times as a relay stop before it is
visited as an overlay peer, thus creating duplicate unnecessary messages to the
network and delaying query responses.
Even though this attempt is based on a simple and elegant solution it is
reported to not guarantee performance in terms of average communication delay
or search scope \cite{HLH2009}.
%
% TODO: SOME DISCUSSION
%
%In a static environment LTM may reduce traffic cost by around 80 to 85 percent
% while SBO reduces traffic cost between 85 and 90 percent. However, LTM  is
%proved to converge in around 2-3 steps while SBO needs 4-5 steps. Moreover LTM
%reduces response time by more than 60 percent in 3 steps while SBO needs 8. In
%a dynamic environment (10 minute average peer lifetime, 0.3 queries/sec by each
%peer) SBO and LTM reduce the average traffic cost per query (including the
%overhead due to the optimization steps) by 85 and 80 percent, respectively.
%Moreover LTM reduces the response time per query to 30 percent while SBO to 35
%percent.
%
% THE LINES BELOW NEED REWORDING
% ==============================
% \cite{LXN2004} Based on the above discussions, we can see the major
% advantages of using a bipartite overlay. First, the operation
% overhead is reduced. In ACE, every peer is required to
% probe the neighbor distance and compute the MST, whereas
% in SBO, white peers do the probing and red peers do the
% computing. Second, SBO extends ACE into two-hop
% neighbors, without additional information exchange
%
%\cite{ni_mismatch_2004} shows SBO, achieves approximately 85 percent reduction
% on traffic cost and about 60 percent reduction on query response time.
In regards to the $3$ stated criteria, \emph{SBO} behaves as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% SBO reduces traffic cost between 85 and 90 percent
high &
% compared to LTM it has slower convergence speed thus incurs more, total,
% overhead.
medium &
%
medium
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \emph{Innocuous Topology Aware Overlay Construction (ITA)}
approach~\cite{PRFM2009} seeks to offer both an overlay formation approach and
an effective way to carry out searching. When constructing the overlay,
\emph{ITA} exploits the notion of \emph{short} and \emph{long} connections.
Should $N$ be the number of network peers,  $\alpha \leq 1 $ a system-wide magic
number and $x$ an $\alpha$-related latency threshold, the bootstrapping peer
randomly selects $\alpha \ast N$ ``close'' (latency below $x$) and 
$\left( 1 - \alpha \right) \ast N$ distant (latency above $x$) nodes
as its neighbors.
%%QUE how do they select all these magic constants???
%%ANS This α constant seems to be the percentage of close neighbors selected by
% a peer out of its total degree. Can't find the criterion with which it is
% chosen though. Maybe we can ask... Mema :)
Searching occurs in $2$ phases: in the initial, the querying node
floods its distant neighborhood  with \emph{TTL=1}.
Subsequently, peers receiving a query over a ``long link'' commence a 
local flood with \emph{TTL=ttl} where \emph{ttl} is system-defined.
%%QUE how are you supposed to define these parameters?? in a fixed manner??
%%
%%ANS Don't understand... the paper says that for increased awareness we need a
%% small α (page 7). But in the beginning they give that short links (close-by)
%% are given by α*Ν. I guess this gets smaller for smaller α.... Also on
%% page 7 they say they choose α to be 0.1, 0.05 and 0.033 and that
%% this equals to ``10, 20, 30 long and and the same number of short links''.
%% I don't understand how they deduce these numbers. Since short links is given
%% by α*Ν and long by (1-α)*Ν at least the numbers should be different from
%% short and long links...
The main objective of the overlay construction phase is to yield a network that
exhibits low clustering. In turn, this is a beneficial characteristic for
random graphs as it can lead to a larger coverage of peers and at the same time
help reduce duplication of messages travelling around the network. This
combination offers efficient lookups that pose minimal or no negative impact to
other mechanisms possibly employed by the \p\ systems (e.g., $1$-hop replication
or dynamic querying mechanisms). Experimental results in the same paper suggest
a $50$\% reduction in communication latency among peers by cutting off some $20$\%
of the \emph{IP}-level traffic generated.
%%
Regarding the $3$ criteria, \emph{ITA} is placed as follows:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% low clustering with larger coverage of peers with the same number of messages
% and reduced duplication.
medium &
% construction at peer join, while searching using local ``floods''
low &
% the selection of neighbors is done at join time. No overlay adaptation means
% low scalability in dynamic environments.
medium
\end{tabular}
}
\end{center}

@@

Below, we outline how the proposed protocols use elements of the four
methodologies and we offer a summary qualitative comparison for all surveyed
approaches applicable for \emph{unstructured} \p \emph{systems}.
Moreover, Table~\ref{unstructured:table} offers a summary overview for each effort;
in particular, the Table shows which of the aforementioned methodologies 
every effort incorporates, the highlights of the effort as well as 
a rough estimation of the pros and cons of in its implementation.

>>>>

The \emph{Scalable Bipartite Overlay (SBO)}~\cite{LXN2007} 
reduces the overhead of creating
and maintaining a minimum spanning tree 
by randomly dividing the nodes into
two groups --\emph{red}s and \emph{white}s-- 
and assigning different tasks to the two groups.
When a peer joins the network, it is randomly assigned with an initial
color (red or white).
Then the network bootstrap host node furnishes the joining peer with a list
of active peers along with their color information. 
The joining peer uses this list to 
establish connections to differently colored peers. 
In this regard, all peers form a a bipartite overlay. 
Using the network delay as a metric, white-peers 
peers measure distances from red counterparts
and report the encountered red neighbors.
Having information on all their $2$-hop neighbors 
($N^2$)
red-peers create minimum spanning trees for the neighbors in question and
assign efficient $2$-hop forwarding paths. This process can render a white
peer $E$ non--forwarding neighbor of the red peer $P$. Direct neighbor
replacement is a process conducted by $E$ in order to replace $P$ with a
$P' \in N^2(P)$ as its new neighbor. This adaptation tackles the
topology mismatch problem by reducing message duplication and shorten response
times caused by the problem identified as \emph{Revisit Not known (RN)}. RN is
the situation when a node is visited some times as a relay stop before it is
visited as an overlay peer, thus creating duplicate unnecessary messages to the
network and delaying query responses.
Even though this attempt is based on a simple and elegant solution it is
reported to not guarantee performance in terms of average communication delay
or search scope \cite{HLH2009}.
%
% TODO: SOME DISCUSSION
%
%In a static environment LTM may reduce traffic cost by around 80 to 85 percent
% while SBO reduces traffic cost between 85 and 90 percent. However, LTM  is
%proved to converge in around 2-3 steps while SBO needs 4-5 steps. Moreover LTM
%reduces response time by more than 60 percent in 3 steps while SBO needs 8. In
%a dynamic environment (10 minute average peer lifetime, 0.3 queries/sec by each
%peer) SBO and LTM reduce the average traffic cost per query (including the
%overhead due to the optimization steps) by 85 and 80 percent, respectively.
%Moreover LTM reduces the response time per query to 30 percent while SBO to 35
%percent.
%
% THE LINES BELOW NEED REWORDING
% ==============================
% \cite{LXN2007} Based on the above discussions, we can see the major
% advantages of using a bipartite overlay. First, the operation
% overhead is reduced. In ACE, every peer is required to
% probe the neighbor distance and compute the MST, whereas
% in SBO, white peers do the probing and red peers do the
% computing. Second, SBO extends ACE into two-hop
% neighbors, without additional information exchange
%
%\cite{ni_mismatch_2004} shows SBO, achieves approximately 85 percent reduction
% on traffic cost and about 60 percent reduction on query response time.
In regards to the $3$ stated criteria, \emph{SBO} behaves as follows:
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% SBO reduces traffic cost between 85 and 90 percent
high &
% compared to LTM it has slower convergence speed thus incurs more, total,
% overhead.
medium &
%
medium
\end{tabular}
}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
The \emph{Innocuous Topology Aware Overlay Construction (ITA)}
approach~\cite{PRFM2013} seeks to offer both an overlay formation approach and
an effective way to carry out searching. When constructing the overlay,
\emph{ITA} exploits the notion of \emph{short} and \emph{long} connections.
Should $N$ be the number of network peers,  $\alpha \leq 1 $ a system-wide magic
number and $x$ an $\alpha$-related latency threshold, the bootstrapping peer
randomly selects $\alpha \ast N$ ``close'' (latency below $x$) and 
$\left( 1 - \alpha \right) \ast N$ distant (latency above $x$) nodes
as its neighbors. Of course, the bootstrapping peer is not able check all the
peers in the network to find the global best for the above sets. Authors
prove that latency measurements against $30/ \alpha$ randomly selected peers
result to a good estimation. 
%%QUE how do they select all these magic constants???
%%ANS This α constant seems to be the percentage of close neighbors selected by
% a peer out of its total degree. Can't find the criterion with which it is
% chosen though. Maybe we can ask... Mema :)
Searching occurs in $2$ phases: in the initial, the querying node
floods its distant neighborhood  with \emph{TTL=1}.
Subsequently, peers receiving a query over a ``long link'' commence a 
local flood with \emph{TTL=ttl} where \emph{ttl} is system-defined.
%%QUE how are you supposed to define these parameters?? in a fixed manner??
%%
%%ANS Don't understand... the paper says that for increased awareness we need a
%% small α (page 7). But in the beginning they give that short links (close-by)
%% are given by α*Ν. I guess this gets smaller for smaller α.... Also on
%% page 7 they say they choose α to be 0.1, 0.05 and 0.033 and that
%% this equals to ``10, 20, 30 long and and the same number of short links''.
%% I don't understand how they deduce these numbers. Since short links is given
%% by α*Ν and long by (1-α)*Ν at least the numbers should be different from
%% short and long links...
The main objective of the overlay construction phase is to yield a network that
exhibits low clustering. In turn, this is a beneficial characteristic for
random graphs as it can lead to a larger coverage of peers and at the same time
help reduce duplication of messages travelling around the network. This
combination offers efficient lookups that pose minimal or no negative impact to
other mechanisms possibly employed by the \p\ systems (e.g., $1$-hop replication
or dynamic querying mechanisms). Experimental results in the same paper suggest
a $50$\% reduction in communication latency among peers by cutting off up to 
$25$\% of the \emph{IP}-level traffic generated.
%%
Regarding the $3$ criteria, \emph{ITA} is placed as follows:
%
\begin{center}
{\footnotesize
\begin{tabular}{ccc}
\emph{Efficiency} & \emph{Overhead} & \emph{Scalability} \\
\hline
% low clustering with larger coverage of peers with the same number of messages
% and reduced duplication.
medium &
% construction at peer join, while searching using local ``floods''
low &
% the selection of neighbors is done at join time. No overlay adaptation means
% low scalability in dynamic environments.
medium
\end{tabular}
}
\end{center}

@@

Below, we outline how the proposed protocols use elements of the four
methodologies and we offer a summary qualitative comparison for all surveyed
approaches applicable for \emph{unstructured}~\p~\emph{systems}.
Moreover, Table~\ref{unstructured:table} offers a summary overview for each effort;
in particular, the Table shows which of the aforementioned methodologies 
every effort incorporates, the highlights of the effort as well as 
a rough estimation of the pros and cons of in its implementation.
